A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-10 main.tex
Finish the section of references.

\red{Besides,} multistage calculi also have a long history of research.
Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
However, $\lambda^\circ$ don't have operators for run and CSP.
\red{runはboldか? Besidesより適切な接続詞はないのか?}

Taha and Sheard introduced run and CSP to a multistage calculus in \cite{MetaML}.
Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.
In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multistage calculus with environment classifiers and
show that run can be represented as application of $\epsilon$ to transition abstractions.
In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
which allows us to dump the quoted code into an external file.

@@

		  DTALの定義と制約solverを用いた型検査の定義
	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}

\end{enumerate}

>>>>

\red{Besides,} multistage calculi also have a long history of research.
Davis revealed there is Curry-Howard correspondence between a multistage calculus and modal logic in $\lambda^\circ$\cite{davies1996temporal}.
However, $\lambda^\circ$ don't have operators for run and CSP.
\red{runはboldか? Besidesより適切な接続詞はないのか?}
Benaissa, et al. \cite{benaissa1999logical} study the relationship between multistage calculus and category theory or modal logic.
Taha and Sheard introduced run and CSP to a multistage calculus in \cite{MetaML}.
Additionally, Taha and Nielsen invented the concept of environment classifiers in $\lambda^\alpha$\cite{taha2003environment} and 
construct the type system for $\lambda^\alpha$, which can handle quoting, unquoting, run, and CSP.

In $\lambda^\TW$\cite{Tsukada}, Tsukada and Igarashi found modal logic which corresponds to a multistage calculus with environment classifiers and
show that run can be represented as application of $\epsilon$ to transition abstractions.
In \LTP\cite{Hanada2014}, Hanada and Igarashi extended $\lambda^\TW$ with CSP and discuss code residualization 
which allows us to dump the quoted code into an external file.

@@

		  DTALの定義と制約solverを用いた型検査の定義
	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
	\item Done: Logical Modalities and Multi-Stage Programming\cite{benaissa1999logical}
	% \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
	% \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
	% \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
	% \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
	% \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
	% \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
	% \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
	% \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
\end{enumerate}
